A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-01-21 paper/paper.tex
paper.bib: beef up

\section{Future work}
In the cubical case, we expect the construction to eventually provide a model of (some version of) parametric type theory~\cite{} by adding degeneracies, a hierarchy of universes (as sketched e.g. in a talk by Herbelin at the HoTT-UF workshop for the bridge case~\cite{herbelin-hott-uf}) as well as reasoning modulo permutations~\cite{grandis03}.

By equipping the universe construction with a structure of equivalences , as suggested along the lines of Altenkirch and Kaposi~\cite{}, as well as connections~\cite{}, we expect the parametric model to extend into a model of cubical type theory~\cite{}. A key point in this approach, is that, thanks to the indexed construction, we expect univalence to hold by definition in the model, without requiring any kind of Reedy fibrancy as it would a priori be needed in the fibered case. If these intuitions are correct, this would definitively root cubical type theory on top of iterated parametricity translation.

>>>>

\section{Future work}
In the cubical case, we expect the construction to eventually provide a model of (some version of) parametric type theory~\cite{nuyts17,cavallo19} by adding degeneracies, a hierarchy of universes (as sketched e.g. in a talk by Herbelin at the HoTT-UF workshop for the bridge case~\cite{herbelin-hott-uf}) as well as reasoning modulo permutations~\cite{grandis03}.

By equipping the universe construction with a structure of equivalences , as suggested along the lines of Altenkirch and Kaposi~\cite{altenkirch15}, as well as a structure of connections, we expect the parametric model to extend into a model of cubical type theory~\cite{bezem13}. A key point in this approach, is that, thanks to the indexed construction, we expect univalence to hold by definition in the model, without requiring any kind of Reedy fibrancy as it would a priori be needed in the fibered case. If these intuitions are correct, this would definitively root cubical type theory on top of iterated parametricity translation.
